### 2019-09-06 static/files/syllabus-pdf.Rmd
Add syllabus PDF

---
title: Syllabus
slug: syllabus
citeproc: false
bibliography: ../static/bib/references.bib
csl: ../static/bib/chicago-syllabus-no-bib.csl
---

@@

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/files/syllabus.pdf)
- **Last Updated**: 2019-08-22

<span class="newthought">Econometrics</span> [^courseinfo] is the application of statistical tools to quantify and measure economic relationships in the real world. It uses real data to test economic hypotheses, quantitatively estimate causal relationships between economic variables, and to make forecasts of future events. The primary tool that economists use for empirical analysis is ordinary least squares (OLS) linear regression, so the majority of this course will focus on understanding, applying, and extending OLS regressions.

@@

[^courseinfo]: {-}
  `r blogdown::shortcode("courseinfo")`

@@

<span class="newthought">By the end of this course,</span> you will:

@@

See my [tips for success in this course](/reference#tips).

@@

@@

<span class="newthought">You can find descriptions</span> for all the assignments on the [assignments page](/assignments/).

@@

grading <- tribble(
  ~Grade, ~Range, ~Grade1, ~Range1,
  "A",  "93–100%", "C",  "73–76%",
  "A−", "90–92%", "C−", "70–72%",
  "B+", "87–89%", "D+", "67–69%",
  "B",  "83–86%", "D",  "63–66%",
  "B−", "80–82%", "D−", "60–62%",
  "C+", "77–79%", "F",  "< 60%"
)
```

```{r, echo=F}
knitr::kable(assignments)
```

```{r show-assignments-table, eval=F, echo=FALSE, results="asis"}
assignments_total <- tibble(Assignment = "Total",
                            Points = sum(assignments$Points),
                            Percent = NA)

@@

```{r show-grades-table, echo=FALSE, results="asis"}
grading %>%
  pandoc.table(justify = "lclc", 
               col.names = c("Grade", "Range", "Grade", "Range"))
```

@@

Watch this excellent and accurate video explaining office hours:

<iframe src="https://player.vimeo.com/video/270014784" width="640" height="360" frameborder="0" allow="autoplay; fullscreen" allowfullscreen></iframe>

@@

<span class="newthought">You can find a full schedule</span> with resources for each class meeting on the [schedule page](/schedule/).

>>>>

---
output: 
  pdf_document:
    number_sections: false
    keep_tex: true
    fig_caption: yes
    df_print: kable
    latex_engine: xelatex
    template: template-syllabus.tex
    includes:
      in_header: 
geometry: margin=1in

course: "Econometrics"
coursecode: "ECON 480"
section: ""
author: Dr. Ryan Safner
semester: "[metricsF19.classes.ryansafner.com](http://metricsf19.classes.ryansafner.com)"

email: "safner@hood.edu"
web: "ryansafner.com"
officehours: "TuTh 10:30--11:30 A.M."
office: "Rosenstock Hall 118"
classroom: "Rosenstock Trading Room"
classhours: "TuTh 2:00 P.M.--3:15 P.M."

fontfamily: Fira Sans
mainfont: Fira Sans
fontsize: 12pt
sansfont: "Yanone Kaffeesatz"
monofont: "Fira Code"
mathfont: "Fira Sans"

# bibliography: 306syllabus.bib
---

@@

> "There are three kinds of lies: lies, damned lies, and statistics." -- Benjamin Disraeli

**Econometrics** is the application of statistical tools to quantify and measure economic relationships in the real world. It uses real data to test economic hypotheses, quantitatively estimate causal relationships between economic variables, and to make forecasts of future events. The primary tool that economists use for empirical analysis is ordinary least squares (OLS) linear regression, so the majority of this course will focus on understanding, applying, and extending OLS regressions.

@@

@@

**By the end of this course,** you will:

1. apply the models of microeconomics (constrained optimization and equilibrium) towards explaining real world behavior of individuals, firms, and governments
2. explore the effects of economic and political processes on market performance (competition, market prices, profits and losses, property rights, entrepreneurship, market power, market failures, public policy, government failures)
3. apply the economic way of thinking to real world issues in writing

@@

See my [tips for success in this course](http://metricsf19.classes.ryansafner.com/reference#tips).

@@

You can find all course materials at my academic website dedicated for (all sections of) this course [microf19.classes.ryansafner.com](http://microf19.classes.ryansafner.com).

My lecture slides will be shared with you, and serve as your primary resource, but our main "textbook" below is **recommended** as the next best resource and will be available from the campus bookstore.

@@

**You can find descriptions** for all the assignments on the [assignments page](http://metricsf19.classes.ryansafner.com/assignments/).

@@

grading <- tribble(
  ~Grade, ~Range, ~Grade1, ~Range1,
  "A",  "93–100%", "C",  "73–76%",
  "A−", "90–92%", "C−", "70–72%",
  "B+", "87–89%", "D+", "67–69%",
  "B",  "83–86%", "D",  "63–66%",
  "B−", "80–82%", "D−", "60–62%",
  "C+", "77–79%", "F",  "< 60%"
)
```
\begin{center}
```{r, echo = F, results="asis"}
knitr::kable(assignments, format="latex", booktabs=TRUE)
```
\end{center}
```{r show-assignments-table, eval=F, echo=FALSE, results="asis"}
assignments_total <- tibble(Assignment = "Total",
                            Points = sum(assignments$Points),
                            Percent = NA)

@@

\begin{center}
```{r show-grades-table, echo=FALSE, results="asis"}
grading %>%
  knitr::kable(., format="latex", booktabs=TRUE)
```
\end{center}

@@

Watch the excellent and accurate video explaining office hours (on website syllabus page):

@@

**You can find a full schedule** with resources for each class meeting on the [course website schedule page](http://metricsF19.classes.ryansafner.com/schedule/).
